% 首先，选择文档类型。我们用 book 文档类来展示最完整的功能。
\documentclass{book}

% -------------------------
% 导言区：设置宏包和文档信息
% -------------------------

% 设置书名、作者和日期。
\title{My First \LaTeX{} Book}
\author{Gemini \thanks{A special thanks to the LaTeX community!}\and Hanbin Zheng}
\date{\today}

% -------------------------
% 正文开始
% -------------------------
\begin{document}

% -------------------------
% 前言部分：使用罗马数字页码，章节不编号
% -------------------------
\frontmatter
\include{preface} % 从preface.tex里导入
\maketitle % 生成标题页
\tableofcontents % 生成目录

\chapter*{Preface} % 使用星号变体，不编号、不进入目录
This is the preface to the book. It sets the stage for what is to come. We use an unnumbered chapter here.

% 手动将前言标题添加到目录中
\addcontentsline{toc}{chapter}{Preface}

% -------------------------
% 正文部分：页码从1开始，章节正常编号
% -------------------------
\mainmatter

\chapter{Introduction to My Book}
This is the first chapter of the main body of the book. We will introduce all the key concepts here.

\section{First Section}
This is the first section of the introduction. It provides an overview of the topic.
Here is some random text to fill the page and demonstrate page numbers.
\begin{enumerate}
    \item This is a list item.
    \item Another list item.
\end{enumerate}

\subsection{First Subsection with Short Title}
This is a subsection.
\subsubsection{A Deeper Dive}
A further breakdown of the subsection.
\paragraph{A small paragraph.} This is a small, unnumbered paragraph.
\subparagraph{Another tiny paragraph.} This is an even smaller paragraph.

\chapter{The Second Chapter}
This chapter dives deeper into the subject matter.

\section{Section with an Optional Title}
This is a section where we use a short title for the table of contents.
\section[Short Title]{This is a very long and descriptive title for my second section}
Here is some more content for this section.

% -------------------------
% 附录部分：章节编号改为大写字母
% -------------------------
\appendix
\chapter{Appendix A: Supporting Information}
This is the appendix, where we provide additional information that is not essential to the main text.

% -------------------------
% 后记部分：不编号，继续阿拉伯数字页码
% -------------------------
\backmatter
\chapter*{Epilogue}
This is the epilogue of the book. It concludes the story and offers some final thoughts.

% 手动将后记标题添加到目录中
\addcontentsline{toc}{chapter}{Epilogue}

\end{document}
